Analyzing DECREASE trials for extent of data fabrication

### 2016-03-11 submission/manuscript.Rmd
Add computation of ln(RR)

# Step 1: replicating Bouri et al. (2014)

>>>>

# Step 1: reproducing Bouri et al. (2014)

```{r, echo = FALSE}
suppressPackageStartupMessages(if(!require(metafor)){install.package('metafor')})
suppressPackageStartupMessages(library(metafor))

bouri_data <- read.csv('../data/bouri_data.csv')

bouri_data$a <- bouri_data$control_n - bouri_data$control_events
bouri_data$b <- bouri_data$beta_n - bouri_data$beta_events
bouri_data$c <- bouri_data$control_events
bouri_data$d <- bouri_data$beta_event

# Add .5 to studies with zero-counts
bouri_data[c(4, 7, 9), 7:10] <-  bouri_data[c(4, 7, 9), 7:10] + .5

bouri_data$ln_rr <- log((bouri_data$d/(bouri_data$b+bouri_data$d))/(bouri_data$c/(bouri_data$a+bouri_data$c)))
bouri_data$se_ln_rr <- sqrt((1/bouri_data$a)+(1/bouri_data$b)+(1/bouri_data$c)+(1/bouri_data$d))
```
